---
title: "NOSO MFI data collection Trend"
author: 
  Idrissa DABO
title-block-banner: "#D7DBDD"
date-modified: "09/04/2024 10:30"
date-format: "MM/D/YYYY, HH:mm"
lang: fr
language: 
  title-block-author-single: "RAM Officer"
  title-block-modified: "Last update"
format: 
  html:
    self-contained: true
    toc: true
    toc-location: right
editor: visual
---

## Data Collected Overview


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(gtsummary)
library(wordcloud)
library(tm)
library(DT)

# data <- read_sav("C:\\Users\\USER MSI\\Documents\\WFP\\Cameroon CO\\Market Monitoring\\NOSO Mission\\Tendance/data.sav") %>% labelled::to_factor()

data <- read_sav("data.sav") %>% labelled::to_factor()

data <- data |> rename(
  Region = TrdNodDensLocNameAdm1,
  Departement = TrdNodDensLocNameAdm2
)

total_data <- data %>%
  group_by(Region, Departement, MarketName, SvyMod) %>%
  count() |>filter(SvyMod == "Trader") |> filter(n < 12)
 
tableau2 <- data %>%
   tbl_summary(include = c("Region", "Departement", 
                            "MarketName"), by = SvyMod, percent = "row")%>%
  add_overall(last = TRUE, col_label = "**Ensemble** (effectif total: {N})")

data2 <- data

text <- data2$UOAPriceIncr_expln

docs <- Corpus(VectorSource(text))

# Cleaning the vector
# 
# gsub("https\\S*", "", text) 
# gsub("@\\S*", "", text) 
# gsub("amp", "", text) 
# gsub("[\r\n]", "", text)
# gsub("[[:punct:]]", "", text)
# 
# docs <- docs %>%
#   tm_map(removeNumbers) %>%
#   tm_map(removePunctuation) %>%
#   tm_map(stripWhitespace)
# docs <- tm_map(docs, content_transformer(tolower))
# docs <- tm_map(docs, removeWords, stopwords("english"))

# Creating the dictionary

# dtm <- TermDocumentMatrix(docs) 
# matrix <- as.matrix(dtm) 
# words <- sort(rowSums(matrix),decreasing=TRUE) 
# df <- data.frame(word = names(words),freq=words)

# set.seed(1234) # for reproducibility 
# wordcloud(words = df$word, freq = df$freq, min.freq = 1, max.words = 200, random.order=FALSE, 
#           rot.per = 0.35, colors = brewer.pal(8, "Dark2"))

```



There is 229 questionnaires (203 trader and 26 Market)  collected in North West and 174 questionnaires (156 trader and 18 Market) collected in South-West. The trend 
```{r echo=FALSE}
tableau2
```

## Market with less than 12 traders collected
There is 15 markets where the number of trader questionnaire collected is less than 12
```{r echo=FALSE}
datatable(total_data)
```

## Size of shops in NOSO
 Among the trader  surveyed  7.2% have Big shop, 26% have Normal Shop, 25% have small shop and 41% have Single staff. the number of check-out points or cashiers operate varies between 1 and 3, 90% of which have only one chect out point

```{r echo=FALSE}
data %>%
  tbl_summary(include = c("ShopSize",  "ShopCheckoutNb"), 
              by = SvyMod)%>%
  add_overall(last = TRUE, col_label = "**Ensemble** (Total: {N})")

```


## Cereals Food item normally sold
```{r echo=FALSE}
data %>% 
  select(contains("UOASoldGroup_FCer.")) %>% 
  tbl_summary()
```

## Other food except cereal food normally sold
```{r echo=FALSE}
data %>% 
  select(contains("UOASoldGroup_FOth.")) %>% 
  tbl_summary()
```

## Non-Food item normally sold
```{r echo=FALSE}
data %>% 
  select(contains("UOASoldGroup_NF.")) %>% 
  tbl_summary()
```

## number of distinct items on sale in Market
Out of the 44 markets, 20% have more 1000 items, 30% between 201 to 1000, 34% between 51 to 200 and 16% less than 50 items
```{r echo=FALSE}
data %>% 
   select(MktTrdSkuNb_Cl) %>%  
   tbl_summary()

```

